Assessment of the KLGO Coastal Waterbird Survey Monitoring Program

### 2018-11-28 analysis/paper/paper.Rmd
some of the graph data from over break.
Added some to paper.rmd. Also, part 2 of script changes, although it won't knit as is.

@@

###Analysis Design
Priority 
Summaries of interest 
(tie to Conceptual Model and Information Objectives)
Associated analyses
Reporting schedule
Questions: Who does the analyses? Interest in setting up as Reproducible Research draft report? 
General delay in reporting? When normally completed?

>>>>

```{r}
source("../scripts/data_exploration.R")
```

@@

###Analysis Design
Priority 
Summaries of interest 
(tie to Conceptual Model and Information Objectives)
Associated analyses:

Number of species sighted per year: 2003-2016 (source 2 found 2003-2009)
.Waterbird and non-waterbird species
.Positive association between species richness and year of survey, when excluding year 2014, which started later than usual. R-squared = .54.
.Species richness within year: 2016
.Individual and max. numbers of observed counts for each species for year 2016, with first and last sightings noted.
.Peak abundance/species richness identified with observed species counts and individual sightings across surveys during 2016 season
.Peak abundance (May 4) observed to be in tandem with spring euchalon (April 21-)
.Species richness peaked May 4-11

Observer bias: variation in number of surveys and length of monitoring season
.2010: No seasonal technician; only sporadic surveys
.2014: Surveys begun 1 month late (May 22)
.Across years: observer turnover rate, varying experience

Number of surveys across census units per year (2003-2009) & distribution of survey dates

Percent of expected waterbird and breeding landbird species (174) confirmed (158; 91%)

Diversity
.Simpson’s Diversity Index (1/D) (2003-2009): heavily sensitive to species richness
.Q statistic (2003-2009)
.Simpson evenness measure: (1/D)/# species, where values approaching 1 signal more equal distribution (not sensitive to species richness)

Comparisons across census units:
.Unit characteristics
.Area of unit (square km)
.Shoreline habitat (meters)
.Waterbird characteristics:
.Average number of waterbirds per survey per square km
.Diversity measures
Analysis across dates each year:
.Number of species; number of birds
.Diversity measures

Reporting schedule
Questions: Who does the analyses? Interest in setting up as Reproducible Research draft report? 
General delay in reporting? When normally completed?
